Generalized Linear Mixed Effects Models

### 2024-05-23 examples/6_Examples_GeneralizedEstimatingEquations.qmd
updates ex 5-10

library(tidyverse)    # Collection of R packages for data science
library(rstatix)      # Pipe-friendly framework for basic statistical tests
library(geepack)      # Generalized Estimating Equations (GEE) analysis

@@

# Generate the plot
ggplot(predicted_values, aes(x = event, y = mean_height)) +
  geom_line(color = "blue", size = 1) +
  geom_point(color = "blue", size = 3) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2, color = "blue") +
  labs(
    title = "Mean Height Across Time Points with Confidence Intervals (GEE)",
    x = "Time Point",
    y = "Mean Height (inches)"
  ) +
  theme_minimal()

>>>>

library(tidyverse)    # Collection of R packages for data science
library(rstatix)      # Pipe-friendly framework for basic statistical tests
library(geepack)      # Generalized Estimating Equations (GEE) analysis
library(gtsummary) # Publication-ready tables

@@

# Generate the plot
ggplot(predicted_values, aes(x = event, y = mean_height)) +
  geom_line(color = "blue", linewidth = 1) +
  geom_point(color = "blue", size = 3) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2, color = "blue") +
  labs(
    title = "Mean Height Across Time Points with Confidence Intervals (GEE)",
    x = "Time Point",
    y = "Mean Height (inches)"
  ) +
  theme_minimal()

### 2024-05-23 examples/7_Examples_GeneralizedLinearMixedEffectsModels.qmd
updates ex 5-10

library(tidyverse)    # Collection of R packages for data science
library(rstatix)      # Pipe-friendly framework for basic statistical tests
library(lme4)         # Linear mixed-effects models

@@

# Fit the LMM model
model <- lmer(height ~ 1 + event + (1 | id), data = df_long, REML = TRUE)

# Extract fixed effects
fixed_effects <- fixef(model)

summary(model)
summary(fixed_effects)

@@

# Prepare data frame for plotting
df_long$predicted_height <- predict(model, re.form = NA) # Overall fixed effect predictions

# Calculate individual intercept adjustments
df_long$individual_intercept <- predict(model, re.form = ~ (1 | id)) - fixed_effects[1]

# Combine fixed effects and random effects predictions
df_long$combined_predicted_height <- df_long$predicted_height + df_long$individual_intercept

# Generate the plot
ggplot(df_long, aes(x = event, y = height)) +
  geom_point(alpha = 0.3) +
  geom_line(aes(y = combined_predicted_height, group = id), color = "grey", alpha = 0.5) +
  geom_line(aes(y = predicted_height, group = 1), color = "blue", size = 1.5) +
  labs(
    title = "Predicted vs. Observed Heights with GLMM",
    x = "Event",
    y = "Height (inches)"
  ) +
  theme_minimal()

>>>>

library(tidyverse)    # Collection of R packages for data science
library(rstatix)      # Pipe-friendly framework for basic statistical tests
library(lme4)         # Linear mixed-effects models
library(gtsummary) # Publication-ready tables

@@

# # Fit the GLMM model
# model <- lmer(handedness ~ 1 + event + (1 | id), data = df_long, REML = TRUE)
# 
# # Extract fixed effects
# fixed_effects <- fixef(model)
# 
# summary(model)
# summary(fixed_effects)

@@

# # Prepare data frame for plotting
# df_long$predicted_height <- predict(model, re.form = NA) # Overall fixed effect predictions
# 
# # Calculate individual intercept adjustments
# df_long$individual_intercept <- predict(model, re.form = ~ (1 | id)) - fixed_effects[1]
# 
# # Combine fixed effects and random effects predictions
# df_long$combined_predicted_height <- df_long$predicted_height + df_long$individual_intercept
# 
# # Generate the plot
# ggplot(df_long, aes(x = event, y = height)) +
#   geom_point(alpha = 0.3) +
#   geom_line(aes(y = combined_predicted_height, group = id), color = "grey", alpha = 0.5) +
#   geom_line(aes(y = predicted_height, group = 1), color = "blue", size = 1.5) +
#   labs(
#     title = "Predicted vs. Observed Heights with GLMM",
#     x = "Event",
#     y = "Height (inches)"
#   ) +
#   theme_minimal()
